Asteroseismology of GD358 with complex C/O core profiles

### 2016-03-03 msnew.tex
Some updates to manuscript

\begin{abstract}
We report on the analysis 33 years (1982-2015) of photometric observations of the pulsating
helium atmosphere white dwarf GD358.  The data set includes 1105.1 hours of new observations
from 2007-2015. From this data set, we extract 15 frequencies representing a sequence 
of radial pulsation modes, adding 4 modes to the 11 modes known previously. We present evidence 
that these 15 modes are $\ell=1$ modes, 13 of which belong to a consecutive sequence in radial overtone
$k$. We perform a detailed asteroseismic analysis using models that include parameterized, complex carbon and oxygen 
core composition profiles to fit the periods.Our results indicate.....

@@

\section{Astrophysical Context}
\label{intro}
White dwarfs are the end product of evolution for around 98\% of the stars in our Galaxy. 
Buried in their interiors are the records of physical processes that take place during 
earlier stages in the life of the star. Nuclear reaction rates during the core helium 
burning phase set the core composition of white dwarfs, while the relative time spent 
burning hydrogen and helium during the asymptotic-giant-branch (AGB) phase and mass-loss 
episodes determine the thickness of the helium layer \citep{Lawlor06,Althaus05}. Helium 
atmosphere white dwarfs (DBs) comprise roughly 20\% of the population of field white 
dwarfs, with most of the remaining 80\% consisting of their hydrogen atmosphere (DA) 
cousins. The bifurcation into two spectral classes is thought to occur during post-AGB 
evolution when, in some cases, a very late thermal pulse burns off the residual hydrogen 
in the envelope, producing a nearly pure helium atmosphere \citep{Iben83}. Such objects 
are then supposed to return to the white dwarf cooling track as PG 1159 stars, which are 
widely believed to be the precursors of most DB white dwarfs. DBs are found to pulsate at 
effective temperatures ranging between 21,000 K and 28,000 K \citep{Beauchamp99, Castanheira05}.

@@

Paradoxally, among the DBVs with enough detected periods to be fitted 
asteroseismically, GD358 is the only one that has not been analyzed using the complex 
C/O profiles adapted and parameterized from stellar evolution calculations
(e.g. {}\citet{Salaris97,Althaus05}). The most recent fits of GD358 \citep{Metcalfe03c} were 
performed using 11 observed modes and simple models where the oxygen abundance 
drops linearly from its central value to zero. We present a new detailed asteroseismic analysis of GD358, taking advantage of 
its long sequence of $\ell=1$ modes to better constrain the asteroseismic fits and 
define the limits of high precision white dwarf asteroseismology.

The present analysis allows us to place GD358 in the context of stellar evolution. 
According to the models, the precursors of DBs emerge from the born-again phase with 
envelopes containing a nearly uniform mixture of helium (He), carbon (C), and oxygen (O) 
out to the photosphere \citep{Dreizler98,Herwig99}. As the PG 1159 stars cool, the helium 
diffuses upward and gradually accumulates to form a chemically pure surface layer. Through 
the DBV instability strip, this process is still ongoing so that instead of a pure helium 
layer surrounding the carbon and oxygen core, one has a region where the carbon and helium 
are still mixed. This leads to a double layered structure, with the pure He surface layer 
overlying the remainder of the uniform He/C/O envelope, all above the degenerate C/O core. 
A key prediction of the diffusion models is that, for a given stellar mass, the pure He 
surface layer will steadily grow thicker as the DB star cools.  GD358 is the fourth DBV 
we can use to check this theory. The other three DBVs 
(\citet{Bischoff-Kim14,Sullivan08, Metcalfe03c}) have painted a picture qualitatively consistent with 
the diffusion calculations, with the hotter best fit models having thinner pure helium 
layers. With GD358, we seek to confirm this trend.

@@

GD358 was discovered in 1982 \citep{Winget82} and has been the target of the Whole 
Earth Telescope (WET) in 1990, 1994, 2000, and 2006 \citep{Provencal09, Kepler03,Winget94}. 
New observations presented here include 254 individual observing runs (1105.1 hrs) spanning 
2007-2015 (Table \ref{journal}). Each season of observations was obtained as part of 
multisite WET campaigns.

Standard WET procedure calls for observers to transfer raw images and 
calibration files to WET headquarters for analysis at the end of each local night. CCD 
data reduction follows the steps described in \citet{Provencal12}. In brief, the new observations 
were obtained with different CCD photometers, each with distinct effective bandpasses. 
We minimize the bandpass issues by using CCDs with similar detectors whenever possible and 
employing a red cutoff filter (BG40 or S8612) to normalize wavelength response and 
reduce extinction effects. We corrected each image for bias and thermal noise, and 
normalized by the flat field. Aperture photometry using the Maestro photometry pipeline 
described by \citet{Dalessio10} was performed on each image, utilizing a range of 
aperture sizes for the target and comparison stars. For each individual nightly run, we 
chose the combination of aperture size and comparison star(s) producing the highest 
signal/noise light curve.

We used the WQED pipeline \citep{wqed} to examine each nightly light curve for photometric 
quality, remove outlying points, divide by suitable comparison stars, and correct for 
differential extinction. Our observational technique is therefore not sensitive to 
oscillations longer than a few hours. The result is a series of light curves 
with amplitude variations represented as fractional intensity (mmi). The unit is a linear 
representation of the fractional intensity of modulation (1 mmi $\approx$ 1 mmag). We present
our Fourier transforms (FTs) in units of modulation amplitude 
($1 {\rm mma}=1 \times 10^{-3} {\rm ma} = 0.1 \% = 1 {\rm ppt}$).

@@

\begin{figure}
\epsscale{0.7}
\plotone{terskol}
\caption{Light curve of GD358 obtained with the Peak Terskol 2.0m.  Each point corresponds 
to a 10 s exposure. The nonlinear, multiperiodic nature of this star is clearly evident.
\label{tersk}
}
\end{figure}

The result is a series of new light curves for each observing season between 2007 and 2015. 
2007 contains 8.1 hrs of observation, 2008 26.1 hrs, 2009 45 hrs, 2010 201.3 hrs, 2011 
401.1 hrs, 2012 150.5 hrs, 2013 87 hrs, 2014 184.6 hrs, and 2015 55 hrs. Our coverage is 
not complete, and this incompleteness produces spectral leakage in the amplitude spectra. 
To quantify this, we sampled single sinusoids using exactly the same times as the original 
data for each season. The resulting amplitude spectrum, or ``spectral window'', is the 
pattern produced in the FT by a single frequency. The FTs for 2010, 2011, and 2014 
are given in Fig.~\ref{fts}.

\begin{figure}
\plotone{gd358multidft}
\caption{Fourier Transforms of GD358 for the 2010, 2011, and 2014 observing seasons.
The frequency range of the observed series of $\ell=1$ modes discussed in section \ref{analysis} 
is indicated by the left arrow (red).  Peaks below $\approx$ 2400 \muHz\ are combination 
frequencies discussed in section \ref{analysis} (right arrow, blue). 
(A color version of this figure is available in the online journal.)
\label{fts}
}
\end{figure}

@@

Our goal is to compile a complete list of GD358's observed independent and combination frequencies 
to be used in a comprehensive asteroseismic analysis. GD358 is known for large scale changes in 
amplitudes and small but not insignificant frequency variations on a variety of timescales 
\citep{Provencal09}.  The amplitude and frequency variations evident in Fig.~\ref{fts} will 
produce artifacts in FTs, greatly complicating any frequency analysis.  
We reanalyzed all available archival data \citep{Provencal09, Kepler03, Winget94, Winget82} 
as well as our new observations to insure continuity in methodology.  We use 
{\sl Period04} \citep{Lenz05} for Fourier analysis and nonlinear least squares fitting to 
select statistically significant peaks in each FT.  As discussed in \citet{Provencal12}, 
we adopt the criterion that a peak must have an amplitude at least four times greater than the 
average noise level in the given frequency range. We define ``noise'' as the frequency-dependent 
average amplitude after prewhitening by the dominant frequencies. This is a conservative estimate, 
as it is impossible to ensure that all of the ``real'' frequencies are removed when determining
the noise level. This is certainly true for GD358, where the peaks above $\approx$ 2500 $\mu$Hz\ 
are combination frequencies (see Section \ref{mode}, \citet{Provencal09}).  Fig.~\ref{noise} displays the average noise 
as a function of frequency for the 2007-2015 observing seasons. A similar plot for the 
archival data is presented in Fig. 3 of \citet{Provencal09}. To confirm our uncertainty 
estimates, we calculated Monte Carlo simulations using the routine provided in {\sl Period04}.  
This routine generates a set of light curves using the original times, the fitted frequencies and 
amplitudes, and added Gaussian noise. A least squares fit is performed on each simulated light 
curve, with the distribution of fit parameters giving the uncertainties. Our Monte Carlo results 
are consistent with our average noise estimates.

@@

Our frequency selection procedure involves identifying the largest amplitude resolved peak in the FT,
fitting a sinusoid at that frequency to the data set, subtracting the fit from the light curve, 
recomputing the FT, examining the residuals, and repeating the process until no significant power 
remains. This technique, known as prewhitening, must be employed with an over-abundance of caution, 
especially since we are aware of amplitude and/or frequency modulation in our data set. A detailed
discussion of the prewhitening procedure and steps taken to minimize the effects of amplitude 
modulation is given in \citep{Provencal09}. Our final identifications of independent frequencies
detected in each observing season are given in Table \ref{freq1} and Table \ref{freq2}.

@@

Fig.~\ref{schematic} presents a schematic representation of GD358's 
independent frequencies detected between 1982 and 2015.  
The features of asteroseismic importance are the localized bands between 900 and 2400
\muHz\ (1100 and 400 s). We interpret each band to represent a single radial overtone. The bands
themselves illustrate the second way in which GD358's frequencies vary. Each band consists of 
frequency detections from multiple observing seasons, but each band is significantly wider in 
frequency space than the frequency error of any single measurement, arguing that some process 
is acting on the frequencies. The simplest explanation is rotational splitting.  However, with the 
exception of the two highest frequency (shortest period) bands ($k=8$ and $k=9$ 
from \citet{Provencal09}), we find no clear evidence of multiplet structure in the frequency 
distributions of the lower frequency (longer period) bands (Fig.~\ref{rot}). The lower frequency band widths are 
most likely the result of amplitude and/or frequency modulation that obscures any underlying 
signatures of rotational splitting.

\begin{figure}
 \epsscale{1.0}
 \plotone{gd358k17_k8.eps}
% \plottwo{gd358multifk17.eps}{gd358multifk8.eps}
 \caption{The detailed schematic distribution of frequencies for the bands near 1300({\em{right}}
 and 2360 \muHz\ ({\em{left}}). The 1300 \muHz\ band shows no multiplet structure, unlike the 2360 \muHz\
 band. Here we see clear evidence of multiplet structure. Assuming the triplet structure represents
 $\ell=1$, this implies a rotation period of $\approx 1.5$ days. Note changes in the scale for both axes.
 (A color version of this figure is available in the online journal.)
 \label{rot}}
\end{figure}

Fig. \ref{schematic} also shows that the widths of the bands is not constant, but changes from band to band.
\citet{Bell15} presents an interesting analysis of the hydrogen atmosphere pulsator (DAV) KIC4552982, 
in which they identify 17 bands of pulsation frequencies. This DAV follows the general pattern exhibited 
by GD358: the highest frequency (shortest period) mode shows evidence of rotational splitting, while the 
lower frequency (longer period) modes are complex bands. The authors note that this DAV's bands have 
different widths in frequency space, and that there may be astronomical significance to this. Although the 
observational timebases and coverage are quite different (20 continuous months for KIC4552982 vs 30 
incomplete years for GD358), our data presents the opportunity to investigate this for a DB pulsator.  
We measured the width of each of GD358's band. We define ''width'' as the difference between the 
lowest and highest frequency detected in each band. Fig. \ref{thick} presents the results. 
The widths of GD358's bands are commensurate with those found in KIC4552982.  We also find a general 
increase in width with decreasing frequency (increasing period), until we reach 
the mode at 1238 \muHz\ (807 s). This band has a width at least twice as wide as any other.

A second interesting pattern is given by the distribution of amplitudes for the modes.  In particular, the 
two modes at 2007.6 and 1857.7 \muHz\ have never been observed at amplitudes above 4 mma.  Interestingly, the 
mode at 1741.5 \muHz\ was not observed at large amplitude prior to 2006.  This ``zone of avoidance'' is telling 
us something about the structure of the star. Lower frequency modes preferentially sample the outer layers of 
the star.  
\begin{figure}
 \epsscale{0.8}
 \plotone{modethick.eps}
 \caption{Width of each bank of power in Fig.~\ref{schematic}. We find an overall increase 
 in band thickness with decreasing frequency (increasing period).  The band at 807~s has a width
 at least twice as large as other bands.  
 \label{thick}}
\end{figure}

@@

Fig.~\ref{modeamps} shows the resulting probability distribution of $\ell$ and $m$ values for the 1735.96 \muHz\
frequency as detected in 2014. The mode is clearly identified as an $\ell=1$, $m=1$ mode.

\begin{figure}
 \epsscale{0.8}
 \plotone{modeamps.eps}
 \caption{Probability distribution (from 0 to 1) of $\ell$ and $m$ values for the 1735.96 variation detected in 
 2014.  The solutions are from individual simulations with $Res_{rms}<9.5^{-06}$. The amplitudes of the 
 observed combination frequencies argue that this is $\ell=1$, $m$=1.  
 \label{modeamps}
 }
\end{figure}

Add table with all l,m ids
%\label{tl}
%isnt' that same as table \ref{gd}?

Finally, given the $l$=1 identification, but the lack of definite multiplet structure, the best way to 
determine the l=0 component for each band is simply to average the frequencies in the bands.  We experimented
with numerous weighting techniques, and determined there is no significant difference in our solutions.  
Our final frequency identification for each band is given in Table~\ref{gd}. We use these periods in our asteroseismic fitting.

@@

The basic method in our asteroseismic fitting consists of calculating grids of white dwarf models and 
running a fitting subroutine to match the periods of the models ($\rm P_{calc}$) with the observed 
periods and calculated residuals using the usual formula

\begin{equation}
\label{fiteq1}
\rm \sigma_{RMS} = \sqrt{\frac{\sum_{1}^{n_{obs}} {(P_{calc}-P_{obs})^2}}{n_{obs}}},
\end{equation}

\noindent where $\rm n_{obs}$ is the number of periods present in the pulsation spectrum.

@@

DBVs are younger than their cooler cousins the DAVs. Time-dependent diffusion calculations 
\citep[e.g.][]{Dehner95,Althaus05} show that at 24{,}000~K, a typical temperature for a DBV, 
the carbon has not fully settled into the core of the star yet. We expect the helium layer to 
be separated into a mixed He/C layer with a pure He layer on top, as shown in Fig. \ref{ffit1}. 
Following \citet{Metcalfe05a}, we adopted and parameterized this structure in our models.

@@

In our asteroseismic fits, we initially varied six parameters; the effective temperature, 
the mass and four structure parameters. There are two parameters associated with the shapes 
of the oxygen (and carbon) core composition profiles: the central oxygen abundance (\xo) and 
the edge of the homogeneous carbon and oxygen core (\qfm, as a fraction of stellar mass. 
For envelope structure, \menv marks the location of the base of the helium layer 
and \mhe the location where the helium abundance rises to $1$ (see Fig. \ref{ffit1}). 
\menv and \mhe are mass coordinates, defined as e.g. $M_{\rm env} = -\log(1 - M(r)/M_*)$, 
where $M(r)$ is the mass enclosed in radius r and $M_*$ is the stellar mass.

@@

We started with a master grid (table \ref{fitt1}) chosen so that it covered all relevant 
area of parameter space and had sufficient resolution to find any region of local minimum in the fitness parameter \citep{Bischoff-Kim11a,Bischoff-Kim14}. We used the minimum resolution that was computationally manageable. The master grid involved the computation 
of 10,483,200 models. We fit simultaneously all 15 periods, requiring all of them to be $\ell=1$ 
modes. A fitness map of this initial fit are shown in the left panel of Fig. \ref{ffit2}, and the parameters of the best fit model are listed in table \ref{fitt1}.

@@

Before we refine the period-by-period fitting optimization, it is worth stepping back and consider 
what we can learn from the average period spacing of GD358. The average period spacing provides an asteroseismic measure of the mass and temperature of the star, independent of the details of 
internal chemical composition profiles. Higher $k$ modes are not strongly trapped in the core and 
according to asymptotic theory, they should be nearly evenly spaced in period. This spacing is 
given by (Unno et al. 1989)

@@

The parameters for our best fit model based on the refined grid are listed in table \ref{fitt1} and the periods of that model in 
Table \ref{gd}. The goodness of fit of the model is \sigrms$=4.22$~s. In Fig. \ref{ffit1}, we show the interior structure of 
the best fit model, with the corresponding \bvf frequency profile.

>>>>

\begin{abstract}
We report on the analysis of 33 years of photometric observations of the pulsating
helium atmosphere white dwarf GD358.  The complete data set includes archival data from 1982-2006, 
and 1105.1 hours of new observations from 2007-2015. From this data set, we extract 15 frequencies 
representing g-mode pulsation modes, adding 4 modes to the 11 modes 
known previously. We present evidence that these 15 modes are $\ell=1$ modes, 13 of which belong to 
a consecutive sequence in radial overtone
$k$. We perform a detailed asteroseismic analysis using models that include parameterized, complex carbon and oxygen 
core composition profiles to fit the periods. Recent spectroscopic analyses place GD358 near the red edge of the DBV instability strip, at 24,000 $\pm$ 500~K and a \logg of 7.8 $\pm$ 0.08 dex. The surface gravity translates to a mass range of 0.455 to 0.540 \msun. Our best fit model is slightly more massive and much hotter (by 2,000~K) than the most recent spectroscopy indicates. We find a pure helium layer mass of $10^{-5.40}$, consistent with a red edge object when compared with other DBVs analyzed using the same models.

@@

\section{Astrophysical Context}
\label{intro}
White dwarfs are the end product of evolution for around 98\% of the stars in our Galaxy. 
Buried in their interiors are the records of physical processes that take place during 
earlier stages in the life of the star. Nuclear reaction rates during the core helium 
burning phase set the core composition of white dwarfs, while the relative time spent 
burning hydrogen and helium during the asymptotic-giant-branch (AGB) phase and mass-loss 
episodes determine the thickness of the helium layer \citep{Lawlor06,Althaus05}. Helium 
atmosphere white dwarfs (DBs) comprise roughly 20\% of the population of field white 
dwarfs, with most of the remaining 80\% consisting of their hydrogen atmosphere (DA) 
cousins. The bifurcation into two spectral classes is thought to occur during post-AGB 
evolution when, in some cases, a very late thermal pulse burns off the residual hydrogen 
in the envelope, producing a nearly pure helium atmosphere \citep{Iben83}. Such objects 
then return to the white dwarf cooling track as PG 1159 stars, which are 
widely believed to be the precursors of most DB white dwarfs. DBs are found to pulsate at 
effective temperatures ranging between 21,000 K and 28,000 K \citep{Beauchamp99, Castanheira05}.

@@

Paradoxally, among the DBVs with enough detected periods to be fitted 
asteroseismically, GD358 is the only one that has not been analyzed using the complex 
C/O profiles adapted and parameterized from stellar evolution calculations
(e.g. {}\citet{Salaris97,Althaus05}). The most recent fits of GD358 \citep{Metcalfe03c} were 
performed using 11 observed modes and simple models where the oxygen abundance 
drops linearly from its central value to zero. We present here a new detailed asteroseismic analysis 
of GD358, taking advantage of its long sequence of $\ell=1$ modes to better constrain 
the asteroseismic fits and define the limits of high precision white dwarf asteroseismology.

The present analysis also allows us to place GD358 in the context of stellar evolution. 
According to the models, the precursors of DBs emerge from the born-again phase with 
envelopes containing a nearly uniform mixture of helium (He), carbon (C), and oxygen (O) 
out to the photosphere \citep{Dreizler98,Herwig99}. As the PG 1159 stars cool, the helium 
diffuses upward and gradually accumulates to form a chemically pure surface layer. Through 
the DBV instability strip, this process is still ongoing so that instead of a pure helium 
layer surrounding the carbon and oxygen core, one has a region where the carbon and helium 
are still mixed. This leads to a double layered structure, with the pure He surface layer 
overlying the remainder of the uniform He/C/O envelope, all above the degenerate C/O core. 
A key prediction of the diffusion models is that, for a given stellar mass, the pure He 
surface layer will steadily grow thicker as the DB star cools.  GD358 is the fourth DBV 
we can use to check this theory. The other three DBVs 
(\citet{Bischoff-Kim14,Sullivan08, Metcalfe03c}) have painted a picture qualitatively consistent with 
the diffusion calculations, with the hotter best fit models having thinner pure helium 
layers. With GD358, we seek to confirm this trend.

@@

GD358 was discovered in 1982 \citep{Winget82} and has been the target of the Whole 
Earth Telescope (WET) in 1990, 1994, 2000, and 2006 \citep{Provencal09, Kepler03,Winget94}. 
New observations presented here include 254 individual observing runs (1105.1 hrs) spanning 
2007-2015 (Table \ref{journal}). Each season of observations was obtained as part of 
multisite WET campaigns \citep{wet90}.

Data reduction follows the steps described in \citet{Provencal12}. In brief, the new observations 
were obtained with different CCD photometers, each with distinct effective bandpasses. 
We minimize the bandpass issues by using CCDs with similar detectors whenever possible and 
employing a red cutoff filter (BG40 or S8612) to normalize wavelength response and 
reduce extinction effects. We corrected each image for bias and thermal noise, and 
normalized by the flat field. Aperture photometry using the Maestro photometry pipeline 
described by \citet{Dalessio10} was performed on each image, utilizing a range of 
aperture sizes for the target and comparison stars. For each individual nightly run, we 
chose the combination of aperture size and comparison star(s) producing the highest 
signal/noise light curve.

We used the WQED pipeline \citep{wqed} to examine each nightly light curve for photometric 
quality, remove outlying points, divide by suitable comparison stars, and correct for 
differential extinction. Our observational technique is therefore not sensitive to 
oscillations longer than a few hours. The result is a series of light curves 
with amplitude variations represented as fractional intensity (mmi). The unit is a linear 
representation of the fractional intensity of modulation (1 mmi $\approx$ 1 mmag). We present
our Fourier transforms (FTs) in units of modulation amplitude 
($1\ {\rm mma}=1 \times 10^{-3}\ {\rm ma} = 0.1 \% = 1\ {\rm ppt}$).

@@

\begin{figure}
\epsscale{0.7}
\plotone{terskol}
\caption{Light curve of GD358 obtained with the Peak Terskol 2.0 m telescope.  Each point corresponds 
to a 10 s exposure. The nonlinear, multiperiodic nature of this star is clearly evident.
(A color version of this figure is available in the online journal.)
\label{tersk}
}
\end{figure}

The complexities associated with GD358's pulsations (see Section \ref{freq}) led us to also 
re-reduce all available archival data \citep{Provencal09, Kepler03, Winget94, Winget82} 
insure continuity in methodology. The final result is a series of light curves 
for each observing season between 1982 and 2015. 
For the new observations, 2007 contains 8.1 hrs of observation, 2008 26.1 hrs, 2009 45 hrs, 
2010 201.3 hrs, 2011 401.1 hrs, 2012 150.5 hrs, 2013 87 hrs, 2014 184.6 hrs, and 2015 55 hrs. 
Our coverage is not complete, and this incompleteness produces spectral leakage in the 
amplitude spectra. To quantify this, we sampled single sinusoids using exactly the 
same times as the original data for each season. The resulting amplitude spectrum, 
or ``spectral window'', is the pattern produced in the FT by a single frequency. 
The FTs for 2010, 2011, and 2014 are given in Fig.~\ref{fts}.

\begin{figure}
\plotone{gd358multidft}
\caption{Fourier Transforms of GD358 for the 2010, 2011, and 2014 observing seasons.
The frequency range of the observed series of $\ell=1$ modes discussed in Section \ref{analysis} 
is indicated by the left arrow (red).  Peaks below $\approx$ 2400 \muHz\ are combination 
frequencies discussed in Section \ref{mode} (right arrow, blue). 
(A color version of this figure is available in the online journal.)
\label{fts}
}
\end{figure}

@@

Our goal is to compile a complete list of GD358's observed independent and combination frequencies 
to be used in a comprehensive asteroseismic analysis. GD358 is known for large scale changes in 
amplitudes and small but not insignificant frequency variations on a variety of timescales 
\citep{Provencal09, Kepler03}.  The amplitude and frequency variations evident in Fig.~\ref{fts} demonstrate that 
it is not feasible to analyze the entire data set as one unit. To minimize the effects of the long term  
amplitude and frequency variations, we analyze the light curves from each observing season individually.

We use {\sl Period04} \citep{Lenz05} for Fourier analysis and nonlinear least squares fitting to 
select statistically significant peaks in each FT. We adopt the criterion that a peak must have 
an amplitude at least four times greater than the average noise level in the given frequency range 
\citep{Provencal12}. We define ``noise'' as the frequency-dependent 
average amplitude after removal of the dominant frequencies. This is a conservative estimate, 
as it is impossible to ensure that all of the ``real'' frequencies are removed when determining
the noise level. This is certainly true for GD358, where the peaks above $\approx$ 2500 $\mu$Hz\ 
are combination frequencies (see Section \ref{mode}, \citet{Provencal09}).  Fig.~\ref{noise} displays the average noise 
as a function of frequency for the 2007-2015 observing seasons. A similar plot for the 
archival data is presented in Fig. 3 of \citet{Provencal09}. To confirm our uncertainty 
estimates, we calculated Monte Carlo simulations using the routine provided in {\sl Period04}.  
This routine generates a set of light curves using the original times, the fitted frequencies and 
amplitudes, and added Gaussian noise. A least squares fit is performed on each simulated light 
curve, with the distribution of fit parameters giving the uncertainties. Our Monte Carlo results 
are consistent with our average noise estimates.

@@

Having established our baseline noise levels, we proceed to frequency selection and identification.
Our frequency selection procedure involves identifying the largest amplitude resolved peak in the FT,
fitting a sinusoid at that frequency to the data set, subtracting the fit from the light curve, 
recomputing the FT, examining the residuals, and repeating the process until no significant power 
remains. This technique, known as prewhitening, must be employed with an over-abundance of caution, 
especially since we are aware of amplitude and/or frequency modulation in our data set. A detailed
discussion of the prewhitening procedure and steps taken to minimize the effects of amplitude 
modulation is given in \citep{Provencal09}. Our final identifications of independent frequencies
detected in each observing season are given in Table \ref{freq1} and Table \ref{freq2}.

@@

Fig.~\ref{schematic} presents a schematic representation of GD358's 
independent frequencies detected between 1982 and 2015.  
The features of asteroseismic importance are the localized bands between 900 and 2400
\muHz\ (1100 and 400 s). We interpret the bands to represent a series of radial overtone $k$. The bands
themselves illustrate the second way in which GD358's frequencies vary. Each band consists of 
frequency detections from multiple observing seasons, but each band is significantly wider in 
frequency space than the frequency error of any single measurement, arguing that some process 
is acting on the frequencies. The simplest explanation is rotational splitting.  However, with the 
exception of the two highest frequency (shortest period) bands ($k=8$ and $k=9$ 
from \citet{Provencal09}), we find no clear evidence of multiplet structure in the frequency 
distributions of the lower frequency (longer period) bands (Fig.~\ref{rot}). The lower frequency band widths are 
most likely the result of some process producing amplitude and/or frequency modulation that obscures 
any underlying signatures of rotational splitting.

\begin{figure}
 \epsscale{1.0}
 \plotone{gd358k17_k8.eps}
% \plottwo{gd358multifk17.eps}{gd358multifk8.eps}
 \caption{The detailed schematic distribution of frequencies for the bands near 1300({\em{right}}
 and 2360 \muHz\ ({\em{left}}). As an example of the higher frequency bands, the 1300 \muHz\ band 
 shows no multiplet structure, unlike the 2360 \muHz\ band. Here we see clear evidence of multiplet 
 structure. Assuming the triplet represents
 $\ell=1$, this implies a rotation period of $\approx 1.5$ days. Note changes in the x scale for both axes.
 (A color version of this figure is available in the online journal.)
 \label{rot}}
\end{figure}

Fig. \ref{schematic} also shows that the widths of the bands are not constant, but change 
from band to band. \citet{Bell15} presents an interesting analysis of the hydrogen atmosphere pulsator 
(DAV) KIC4552982, in which they identify 17 bands of pulsation frequencies. KIC4552982 is one of the 
coolest ZZ Cetis known \citep{Tremblay2013}, and it follows the general pattern exhibited 
by GD358: the highest frequency (shortest period) mode shows evidence of rotational splitting, while the 
lower frequency (longer period) modes are complex bands. The authors note that this DAV's bands have 
different widths in frequency space, and that there may be astronomical significance to this. 
Although the observational timebases and coverage are quite different (20 continuous months 
for KIC4552982 vs 33 incomplete years for GD358), our data presents the opportunity to investigate this 
for a cooler DB pulsator.  We measured the widths of each of GD358's band where we have
more than 10 detections. We define ''width'' as the difference between the lowest and highest frequency 
detected in each band. Fig. \ref{thick} presents the results. We find no correlation of width with number
of detected peaks in each band. Interestingly, the widths of GD358's bands are commensurate with those 
found in KIC4552982. We find a general increase in width with decreasing frequency (increasing period), 
until we reach the band at 1238 \muHz\ (807 s). This band has a width at least twice as wide as any other.

A second interesting behavior is given by the distribution of average amplitudes for the bands 
(Fig~\ref{schematic}. In particular, the two bands at 1857.7 and 2007.6  \muHz\ have never been observed 
at amplitudes above 4 mma. The band at 1369 \muHz\ is also only observed at lower amplitudes. Interestingly, 
the band at 1741.5 \muHz\ was not observed at large amplitude prior to 2006, and it has remained at high 
amplitude since that time.

In broad brush strokes, the observed global pulsations involve the whole star, but each pulsation samples the star
in slightly different ways.  For example, modes with lower frequencies (higher radial $k$ values) preferentially 
sample the outer layers, while modes with higher frequencies (lower radial $k$ values) have outer turning points 
that are farther from the surface, and so sample the deeper interior. It makes intuitive sense that lower 
frequency modes would be affected by processes confined to the outer stellar atmosphere. We speculate that the 
observed band widths and pulsation amplitudes contain information about the convection zone and/or any surface
magnetic field. Further investigation requires guidance from theory.

\begin{figure}
 \epsscale{0.8}
 \plotone{modethick.eps}
 \caption{Width of each bank of power in Fig.~\ref{schematic}. We find an overall increase 
 in band thickness with decreasing frequency (increasing period).  The band at 807~s has a width
 at least twice as large as other bands.  
 \label{thick}}
\end{figure}

@@

As an example, Fig.~\ref{modeamps} shows the probability distribution of $\ell$ and $m$ 
values for the 1735.96 \muHz\ frequency as detected in 2014. To produce the distribution, we ran
the amplitude code \citep{Montgomery10} 1000 times, and selected the results having $Res_{rms}<9.5\times10^{-06}$, 
where $Res_{rms}$ are the root-mean-squared residuals between predicted and observed amplitudes.  
For our example, this mode is clearly preferred as an $\ell=1$, $m=1$ mode. We find similar results for all
modes above 10 mma in the 1990, 1994, 2006, 2010, and 2014 observing seasons. Combining the results from the 
combination frequencies with previous evidence, we are confident that the bands in Fig.~\ref{schematic} represent
a series of $\ell=1$ modes.

\begin{figure}
 \epsscale{0.8}
 \plotone{modeamps.eps}
 \caption{Probability distribution (from 0 to 1) of $\ell$ and $m$ values for the 1735.96 variation detected in 
 2014.  The distribution is produced from 1000 simulations, selecting with $Res_{rms}<9.5^{-06}$. 
 The amplitudes of the observed combination frequencies argue that this is $\ell=1$, $m$=1.  
 \label{modeamps}
 }
\end{figure}

%isnt' that same as table \ref{gd}?

Finally, given the $l$=1 identification and the lack of definite multiplet structure for the higher 
frequency modes, the best way to determine the central frequency for each band is simply to 
average the detected frequencies in the bands.  We experimented with numerous weighting techniques, 
and determined there is no significant difference in our solutions.  Our final frequencies for each band 
are given in Table~\ref{gd}. We use these periods in our asteroseismic fitting.

@@

The basic method in our asteroseismic fitting consists of calculating grids of white dwarf models and 
running a fitting subroutine to match the periods of the models ($\rm P^{obs calc}$) with the observed 
periods $P^{\rm obs}$. Following standard statistical methods, each fit is assigned a fitness parameter calculated the following way:

\begin{eqnarray}
\label{fiteq1}
\sigma_{\rm RMS} = \sqrt{\frac{1}{W} \sum_{1}^{n_{\rm obs}} {w_i(P^{\rm calc}_i-P^{\rm obs}_i)^2}}, \\
W=\frac{n_{\rm obs}-1}{n_{\rm obs}}\sum_{1}^{n_{\rm obs}}w_i
\end{eqnarray}

\noindent where $n_{\rm obs}$ is the number of periods present in the pulsation spectrum and the weights $w_i$ are the inverse square of the uncertainties listed for each period in table \ref{gd}. We note that the two shortest period modes have 6000 times the weight of the longest period mode. Another way to see this is to assume we have a calculated period that matches the highest period mode very poorly, being 20 seconds away. 20 seconds is roughly half the average period spacing for $\ell=1$ modes in the relevant area of parameter space and so it is the worse period fit one can get. In order to have the same impact on $\sigma_{\rm RMS}$, the lowest period mode would have to match to within 0.26 seconds. In essence this is almost ignoring the modes that have a period measurement uncertainty of 0.5~s or more.

@@

DBVs are younger than their cooler cousins the DAVs. Time-dependent diffusion calculations 
\citep[e.g.][]{Dehner95,Althaus05} show that at 24{,}000~K, a typical temperature for a DBV, 
the carbon has not yet fully settled into the core of the star. We expect the helium layer to 
be separated into a mixed He/C layer with a pure He layer on top, as shown in Fig. \ref{ffit1}. 
Following \citet{Metcalfe05a}, we adopted and parameterized this structure in our models.

@@

In our asteroseismic fits, we initially varied six parameters; the effective temperature, 
the mass and four structure parameters. There are two parameters associated with the shapes 
of the oxygen (and carbon) core composition profiles: the central oxygen abundance (\xo) and 
the edge of the homogeneous carbon and oxygen core (\qfm, as a fraction of stellar mass. 
For envelope structure, \menv\ marks the location of the base of the helium layer 
and \mhe\ the location where the helium abundance rises to $1$ (see Fig. \ref{ffit1}). 
\menv\ and \mhe\ are mass coordinates, defined as e.g. $M_{\rm env} = -\log(1 - M(r)/M_*)$, 
where $M(r)$ is the mass enclosed in radius r and $M_*$ is the stellar mass.

@@

We started with a master grid (Table \ref{fitt1}) chosen so that it covered all relevant 
area of parameter space and had sufficient resolution to find any region of local minimum 
in the fitness parameter \citep{Bischoff-Kim11a,Bischoff-Kim14}. We used the minimum resolution 
that was computationally manageable. The master grid involved the computation 
of 10,483,200 models. We fit simultaneously all 15 periods, requiring all of them to be $\ell=1$ 
modes. A fitness map of this initial fit are shown in the left panel of Fig. \ref{ffit2}, and the 
parameters of the best fit model are listed in Table \ref{fitt1}.

@@

Before we refine the period-by-period fitting optimization, it is worthwhile to step back and consider 
what we can learn from the average period spacing of GD358. The average period spacing provides an 
asteroseismic measure of the mass and temperature of the star, independent of the details of 
internal chemical composition profiles. Higher $k$ modes are not strongly trapped in the core and 
according to asymptotic theory, they should be nearly evenly spaced in period. This spacing is 
given by (Unno et al. 1989)

@@

The parameters for our best fit model based on the refined grid are listed in Table \ref{fitt1} and the periods of that model in 
Table \ref{gd}. The goodness of fit of the model is \sigrms$=4.22$~s. In Fig. \ref{ffit1}, we show the interior structure of 
the best fit model, with the corresponding \bvf frequency profile.
